```{r}
temp %>% select(contains(c("embryo_endo_inv", "N_inv_postpollen_success", "N_inv_prepollen_success", "species", "individual", "scaled_N_content_per_packaging_dispersal_success", "prepollen_success_inv", "scaled_N_content_per_prepollination_success", "prepollen_discarded_inv"))) %>% filter(embryo_endo_inv >0) %>% View()

N_inv_prepollen_success =  * ,
      N_inv_prepollen_abort =  * N_content_prepollination_all,  
      N_inv_postpollen_success = pack_disp_success_inv * scaled_N_content_per_packaging_dispersal_success,
      N_inv_postpollen_abort = postpollen_aborted_inv * N_content_postpollination_all

N_inv_all_repro = N_inv_prepollen_success+ N_inv_prepollen_abort + N_inv_postpollen_success + N_inv_postpollen_abort + N_inv_propagules,
      



```

```{r}
nutrients_for_accessory <- SummaryInd %>%
  filter(repro_inv > 0 & !is.na(repro_inv)) %>%
  select(species, individual, seedset, embryo_endo_costs) %>%
  left_join(nutrient_accessory_proportions %>%
              select(species, individual, prop_N_prepollen_success_vs_all_prepollen, prop_N_postpollen_success_vs_all_postpollen,
                     prop_P_prepollen_success_vs_all_prepollen, prop_P_postpollen_success_vs_all_postpollen)) %>%
  left_join(N_inv_successful_units) %>%
  left_join(P_inv_successful_units) %>%
  mutate(N_inv_one_successful_unit = N_inv_per_packaging_dispersal_success + N_inv_per_prepollination_success + N_inv_per_propagule,
         N_prop_pollen_attract_vs_success = N_inv_per_prepollination_success/N_inv_one_successful_unit,
         N_prop_provision_vs_success = N_inv_per_packaging_dispersal_success/N_inv_one_successful_unit,
         P_inv_one_successful_unit = P_inv_per_packaging_dispersal_success + P_inv_per_prepollination_success + P_inv_per_propagule,
         P_prop_pollen_attract_vs_success = P_inv_per_prepollination_success/P_inv_one_successful_unit,
         P_prop_provision_vs_success = P_inv_per_packaging_dispersal_success/P_inv_one_successful_unit) %>%
  write_csv("data/accessory_data_in_nutrient_currency.csv")
```




```{r}
color_family <- c("Proteaceae" = "skyblue2", "Fabaceae" = "#661100", "Rutaceae" = "#117733", "Ericaceae" = "#882255", "Lamiaceae" = "#332288", "Thymelaeaceae" = "red")

accessory_using_nutrients <- read_csv("data/accessory_data_in_nutrient_currency.csv")
 
accessory_using_nutrients_species <- accessory_using_nutrients %>%
  dplyr::filter(seedset > 0) %>%
  dplyr::select(-individual) %>%
  #dplyr::select(species, seedset, embryo_endo_costs) %>%
  dplyr::group_by(species) %>%
  #dplyr::mutate(across(c("seedset", "embryo_endo_costs"), ~mean(.x, na.rm = TRUE))) %>%
  dplyr::mutate(across(c("seedset", "embryo_endo_costs", "prop_N_prepollen_success_vs_all_prepollen", "prop_N_postpollen_success_vs_all_postpollen", "prop_P_prepollen_success_vs_all_prepollen", "prop_P_postpollen_success_vs_all_postpollen", "N_inv_per_packaging_dispersal_success", "N_inv_per_prepollination_success", "N_inv_per_propagule", "P_inv_per_packaging_dispersal_success", "P_inv_per_prepollination_success", "P_inv_per_propagule", "N_inv_one_successful_unit", "N_prop_pollen_attract_vs_success", "P_inv_one_successful_unit", "P_prop_pollen_attract_vs_success", "N_prop_provision_vs_success", "P_prop_provision_vs_success"), ~mean(.x, na.rm = TRUE))) %>%
  dplyr::ungroup() %>%
  dplyr::distinct()
```
## Nitrogen

### N data

```{r}
data <- accessory_using_nutrients_species %>%
  select(species,
         embryo_endo_costs = N_inv_per_propagule,
         seedset,
         prop_prepollen_success = prop_N_prepollen_success_vs_all_prepollen,
         prop_postpollen_success = prop_N_postpollen_success_vs_all_postpollen,
         prop_pollen_attract_vs_success = N_prop_pollen_attract_vs_success,
         prop_provisioning_vs_success = N_prop_provision_vs_success
  ) %>%
left_join(species_full %>% dplyr::select(Abbreviation, Family) %>% dplyr::rename(species = Abbreviation))
```


### Panel 3A. Division with successfully-matured units

```{r}
fit3A <- glm(prop_pollen_attract_vs_success ~ log10(seedset),
             family=gaussian(link="logit"), data =  data)

A <- summary(fit3A)[12] %>% as.data.frame()
pvalueA <- A[2,4] %>% round(2)
RsqrA <- formatC(1 - fit3A$deviance/fit3A$null.deviance, format = "f", digits=2) %>% as.character()
A95 <- parameters::standardize_parameters(fit3A, ci = .95)[2,] %>%
  as.data.frame()
A50 <- parameters::standardize_parameters(fit3A, ci = .5)[2,] %>%
  as.data.frame()

A_parameters <-
  c("model", A95[4], A50[4], A95[2], A50[5], A95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3A <-
  ggplot(data = data, aes(x = seedset, y = prop_pollen_attract_vs_success)) +
    geom_point(aes(col = factor(Family)), size = 2.5) +
    geom_smooth(aes(x=seedset, y = fit3A$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,1), labels = label_log(), breaks = c(.001, .01, .1, 1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
  guides(x.sec = "axis", y.sec = "axis") +
  guides(col = guide_legend(title= "Family")) +
    labs(
      x = "Seeds:ovules (seedset)",
      y = str_wrap("Prop. of successful reproductive biomass to pollen attraction", width = 32)
    ) +
    geom_text(aes(x=.001, y=0.9, label="R^2"), size =4, parse = TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.9, label=paste("    =", RsqrA, ", p=", pvalueA)), size =4, hjust=0, vjust=0) +
    ggtitle("A. Division within successfully-matured units") +
    theme_info
```

### Panel 3B. Seedsize-seedset

```{r}
fit3B <- glm(log10(seedset) ~ log10(embryo_endo_costs), data =  data)

B <- summary(fit3B)[12] %>% as.data.frame()
pvalueB <- B[2,4] %>% round(3)
RsqrB <- formatC(1 - fit3B$deviance/fit3B$null.deviance, format = "f", digits=2) %>% as.character()

B95 <- parameters::standardize_parameters(fit3B, ci = .95)[2,] %>%
  as.data.frame()
B50 <- parameters::standardize_parameters(fit3B, ci = .5)[2,] %>%
  as.data.frame()

B_parameters <-
  c("model", B95[4], B50[4], B95[2], B50[5], B95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3B <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = seedset)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = 10^(fit3B$fitted.values)), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,5.0), labels = label_log(), breaks = c(.001,.01, .1, 1)) +
    scale_y_log10(limits = c(0.001,1), labels = label_log(), breaks = c(.001, .01, .1, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = "Seeds:ovules (seedset)"
    ) +
    geom_text(aes(x=.001, y=0.001, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.001, label=paste("    =", RsqrB, ", p=", pvalueB)), size=4, hjust=0, vjust=0) +
    ggtitle("B. Seed size - seedset relationship") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3C. Seedsize-prop_postpollen_success

```{r}
fit3C <- glm(prop_pollen_attract_vs_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

C <- summary(fit3C)[12] %>% as.data.frame()
pvalueC <- C[2,4] %>% round(4)
RsqrC <- formatC(1 - fit3C$deviance/fit3C$null.deviance, format = "f", digits=2) %>% as.character()
C95 <- parameters::standardize_parameters(fit3C, ci = .95)[2,] %>%
  as.data.frame()
C50 <- parameters::standardize_parameters(fit3C, ci = .5)[2,] %>%
  as.data.frame()

C_parameters <-
  c("model", C95[4], C50[4], C95[2], C50[5], C95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3C <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_pollen_attract_vs_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3C$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,5.0), labels = label_log(), breaks = c(.001,.01, .1, 1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
    guides(x.sec = "axis", y.sec = "axis") +
  scale_color_manual(values = color_family) + 
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of successful reproductive biomass to pollen attraction", width = 32)
    ) +
    geom_text(aes(x=.001, y=0.9, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.9, label=paste("    =", RsqrC, ", p=", pvalueC)), size=4, hjust=0, vjust=0, parse=FALSE) +
    ggtitle("C. Division within successfully-matured units") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3D. Seedsize-prop pollen-attraction to success

```{r}
fit3D <- glm(prop_prepollen_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

D <- summary(fit3D)[12] %>% as.data.frame()
pvalueD <- D[2,4] %>% round(3)
RsqrD <- formatC(1 - fit3D$deviance/fit3D$null.deviance, format = "f", digits=2) %>% as.character()

D95 <- parameters::standardize_parameters(fit3D, ci = .95)[2,] %>%
  as.data.frame()
D50 <- parameters::standardize_parameters(fit3D, ci = .5)[2,] %>%
  as.data.frame()

D_parameters <-
  c("model", D95[4], D50[4], D95[2], D50[5], D95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3D <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_prepollen_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3D$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,5.0), labels = label_log(), breaks = c(.001,.01, .1, 1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of pollen-attraction biomass to successful units", width = 32)
    ) +
    geom_text(aes(x=.001, y=0.9, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.9, label=paste("    =", RsqrD, ", p=", pvalueD)), size=4, hjust=0, vjust=0) +
    ggtitle("D. Division of pollen-attraction investment") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3E. Seedsize-prop provisioning to success

```{r}
fit3E <- glm(prop_postpollen_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

E <- summary(fit3E)[12] %>% as.data.frame()
pvalueE <- E[2,4] %>% round(3)
RsqrE <- formatC(1 - fit3E$deviance/fit3E$null.deviance, format = "f", digits=2) %>% as.character()

E95 <- parameters::standardize_parameters(fit3E, ci = .95)[2,] %>%
  as.data.frame()
E50 <- parameters::standardize_parameters(fit3E, ci = .5)[2,] %>%
  as.data.frame()

E_parameters <-
  c("model", E95[4], E50[4], E95[2], E50[5], E95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3E <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_postpollen_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3E$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,5.0), labels = label_log(), breaks = c(.001,.01, .1, 1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of provisioning biomass to successful units", width = 40)
    ) +
    geom_text(aes(x=.001, y=0.01, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.01, label=paste("    =", RsqrE, ", p=", pvalueE)), size=4, hjust=0, vjust=0) +
    ggtitle("E. Division of provisioning investment") +
    theme_info +
  theme(legend.position = "none")
```

### Combined plot

```{r}
Empty_Grob <- 
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_postpollen_success)) +
  theme_classic() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank()
  )

Figure3N_top_row <- arrangeGrob(Panel3A, Empty_Grob, ncol = 2, widths = c(1.5, 0.5))

Figure3N_bottom_rows <- arrangeGrob(Panel3B, Panel3C, Panel3D, Panel3E, ncol = 2, widths = c(1, 1))

Figure3N <- arrangeGrob(Figure3N_top_row, Figure3N_bottom_rows, nrow = 2, ncol = 1, heights =c(1, 2))

grid::grid.draw(Figure3P)

cowplot::save_plot("ms/Accessory/output/Figure3N.jpg", Figure3N, base_width = 6, base_height = 8.5)

```

## Phosphorus

### Phosphorus data
```{r}
data <- accessory_using_nutrients_species %>%
  select(species,
         embryo_endo_costs = P_inv_per_propagule,
         seedset,
         prop_prepollen_success = prop_P_prepollen_success_vs_all_prepollen,
         prop_postpollen_success = prop_P_postpollen_success_vs_all_postpollen,
         prop_pollen_attract_vs_success = P_prop_pollen_attract_vs_success,
         prop_provisioning_vs_success = P_prop_provision_vs_success
  ) %>%
left_join(species_full %>% dplyr::select(Abbreviation, Family) %>% dplyr::rename(species = Abbreviation))
```


### Panel 3A. Division with successfully-matured units

```{r}
fit3A <- glm(prop_pollen_attract_vs_success ~ log10(seedset),
             family=gaussian(link="logit"), data =  data)

A <- summary(fit3A)[12] %>% as.data.frame()
pvalueA <- A[2,4] %>% round(2)
RsqrA <- formatC(1 - fit3A$deviance/fit3A$null.deviance, format = "f", digits=2) %>% as.character()
A95 <- parameters::standardize_parameters(fit3A, ci = .95)[2,] %>%
  as.data.frame()
A50 <- parameters::standardize_parameters(fit3A, ci = .5)[2,] %>%
  as.data.frame()

A_parameters <-
  c("model", A95[4], A50[4], A95[2], A50[5], A95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3A <-
  ggplot(data = data, aes(x = seedset, y = prop_pollen_attract_vs_success)) +
    geom_point(aes(col = factor(Family)), size = 2.5) +
    geom_smooth(aes(x=seedset, y = fit3A$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.001,1), labels = label_log(), breaks = c(.001, .01, .1, 1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
  guides(x.sec = "axis", y.sec = "axis") +
  guides(col = guide_legend(title= "Family")) +
    labs(
      x = "Seeds:ovules (seedset)",
      y = str_wrap("Prop. of successful reproductive biomass to pollen attraction", width = 32)
    ) +
    geom_text(aes(x=.001, y=0.9, label="R^2"), size =4, parse = TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.001, y=0.9, label=paste("    =", RsqrA, ", p=", pvalueA)), size =4, hjust=0, vjust=0) +
    ggtitle("A. Division within successfully-matured units") +
    theme_info
```

### Panel 3B. Seedsize-seedset

```{r}
fit3B <- glm(log10(seedset) ~ log10(embryo_endo_costs), data =  data)

B <- summary(fit3B)[12] %>% as.data.frame()
pvalueB <- B[2,4] %>% round(3)
RsqrB <- formatC(1 - fit3B$deviance/fit3B$null.deviance, format = "f", digits=2) %>% as.character()

B95 <- parameters::standardize_parameters(fit3B, ci = .95)[2,] %>%
  as.data.frame()
B50 <- parameters::standardize_parameters(fit3B, ci = .5)[2,] %>%
  as.data.frame()

B_parameters <-
  c("model", B95[4], B50[4], B95[2], B50[5], B95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3B <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = seedset)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = 10^(fit3B$fitted.values)), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.000001,0.5), labels = label_log(), breaks = c(.000001, .001, .01, .1)) +
    scale_y_log10(limits = c(0.001,1), labels = label_log(), breaks = c(.001, .01, .1, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = "Seeds:ovules (seedset)"
    ) +
    geom_text(aes(x=.0001, y=0.001, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.0001, y=0.001, label=paste("    =", RsqrB, ", p=", pvalueB)), size=4, hjust=0, vjust=0) +
    ggtitle("B. Seed size - seedset relationship") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3C. Seedsize-prop_postpollen_success

```{r}
fit3C <- glm(prop_pollen_attract_vs_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

C <- summary(fit3C)[12] %>% as.data.frame()
pvalueC <- C[2,4] %>% round(3)
RsqrC <- formatC(1 - fit3C$deviance/fit3C$null.deviance, format = "f", digits=2) %>% as.character()
C95 <- parameters::standardize_parameters(fit3C, ci = .95)[2,] %>%
  as.data.frame()
C50 <- parameters::standardize_parameters(fit3C, ci = .5)[2,] %>%
  as.data.frame()

C_parameters <-
  c("model", C95[4], C50[4], C95[2], C50[5], C95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3C <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_pollen_attract_vs_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3C$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.0001,0.5), labels = label_log(), breaks = c(.0001, .001, .01, .1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
    guides(x.sec = "axis", y.sec = "axis") +
  scale_color_manual(values = color_family) + 
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of successful reproductive biomass to pollen attraction", width = 32)
    ) +
    geom_text(aes(x=.0001, y=0.01, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.0001, y=0.01, label=paste("    =", RsqrC, ", p=", pvalueC)), size=4, hjust=0, vjust=0, parse=FALSE) +
    ggtitle("C. Division within successfully-matured units") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3D. Seedsize-prop pollen-attraction to success

```{r}
fit3D <- glm(prop_prepollen_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

D <- summary(fit3D)[12] %>% as.data.frame()
pvalueD <- D[2,4] %>% round(3)
RsqrD <- formatC(1 - fit3D$deviance/fit3D$null.deviance, format = "f", digits=2) %>% as.character()

D95 <- parameters::standardize_parameters(fit3D, ci = .95)[2,] %>%
  as.data.frame()
D50 <- parameters::standardize_parameters(fit3D, ci = .5)[2,] %>%
  as.data.frame()

D_parameters <-
  c("model", D95[4], D50[4], D95[2], D50[5], D95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3D <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_prepollen_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3D$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.0001,0.5), labels = label_log(), breaks = c(.0001, .001, .01, .1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of pollen-attraction biomass to successful units", width = 32)
    ) +
    geom_text(aes(x=.0001, y=0.9, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.0001, y=0.9, label=paste("    =", RsqrD, ", p=", pvalueD)), size=4, hjust=0, vjust=0) +
    ggtitle("D. Division of pollen-attraction investment") +
    theme_info +
  theme(legend.position = "none")
```

### Panel 3E. Seedsize-prop provisioning to success

```{r}
fit3E <- glm(prop_postpollen_success ~ log10(embryo_endo_costs), data =  data,
           family=gaussian(link="logit"))

E <- summary(fit3E)[12] %>% as.data.frame()
pvalueE <- E[2,4] %>% round(3)
RsqrE <- formatC(1 - fit3E$deviance/fit3E$null.deviance, format = "f", digits=2) %>% as.character()

E95 <- parameters::standardize_parameters(fit3E, ci = .95)[2,] %>%
  as.data.frame()
E50 <- parameters::standardize_parameters(fit3E, ci = .5)[2,] %>%
  as.data.frame()

E_parameters <-
  c("model", E95[4], E50[4], E95[2], E50[5], E95[5]) %>% 
  as.data.frame() %>%
  dplyr::rename(parameter = 1, `2.5%` = 2, `25%`=3, `50%`=4, `75%`=5, `97.5%`=6)

Panel3E <-
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_postpollen_success)) +
    geom_point(aes(col = factor(Family)), size =2.5) +
    geom_smooth(aes(x=embryo_endo_costs, y = fit3E$fitted.values), colour="#CC1A36") + 
    scale_x_log10(limits = c(0.0001,0.5), labels = label_log(), breaks = c(.0001, .001, .01, .1)) +
    scale_y_continuous(limits = c(0,1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_color_manual(values = color_family) + 
    guides(x.sec = "axis", y.sec = "axis") +
    labs(
      x = "Seed size (mg)",
      y = str_wrap("Prop. of provisioning biomass to successful units", width = 40)
    ) +
    geom_text(aes(x=.0001, y=0.01, label="R^2"), size=4, parse=TRUE, hjust=0, vjust=0) +
    geom_text(aes(x=.0001, y=0.01, label=paste("    =", RsqrE, ", p=", pvalueE)), size=4, hjust=0, vjust=0) +
    ggtitle("E. Division of provisioning investment") +
    theme_info +
  theme(legend.position = "none")
```

### Combined plot

```{r}
Empty_Grob <- 
  ggplot(data = data, aes(x = embryo_endo_costs, y = prop_postpollen_success)) +
  theme_classic() +
  theme(
    axis.text = element_blank(),
    axis.ticks = element_blank(),
    axis.title = element_blank(),
    axis.line = element_blank()
  )

Figure3P_top_row <- arrangeGrob(Panel3A, Empty_Grob, ncol = 2, widths = c(1.5, 0.5))

Figure3P_bottom_rows <- arrangeGrob(Panel3B, Panel3C, Panel3D, Panel3E, ncol = 2, widths = c(1, 1))

Figure3P <- arrangeGrob(Figure3P_top_row, Figure3P_bottom_rows, nrow = 2, ncol = 1, heights =c(1, 2))

grid::grid.draw(Figure3P)

cowplot::save_plot("ms/Accessory/output/Figure3P.jpg", Figure3P, base_width = 6, base_height = 8.5)

```
```

